UDEMY COURSE

Prof. Fernando Amaral


1.Create two variables Ana and Paulo and assign them values of their ages, respectively 8 and 12 years old.
Variables must be of integer type. Print on the console "The girl is older" or "The boy is older" as a result of a logic test.
```{r}
Ana=8L;
Paulo= 12L;
ifelse(Ana<Paulo, "O menino é mais velho", "A menina é mais velha")
```
2.

BOD is an existing object in R. Check the class of this object.
```{r}
class(BOD)
```

3.Create a vector that stores numbers from 1 to 10 and later prints the even values
```{r}
x=c(1:10)
for(i in x){
  if(x[i]%%2==0)print(x[i])
}

```

4. women is an existing dataframe in R. Print the last 10 lines
```{r}
tail(women,10)
```

5.Use R's plot function to plot the Sepal.Width and Petal.Length attributes of the Iris dataset. The chart should only print from lines 50 to 100.
```{r}
iris
novaIris= iris[50:100,c(2:3)]
plot(novaIris)
```

6.Create two vectors of equal sizes, add the equivalent positions of the vectors and print the result.
```{r}
vector1= c(2,2,2,2)
vector2=c(2,4,8,16)

for(i in 1:length(vector1)){
  result=vector1[i]+vector2[i]
  print(result)
}
```


7.Print the number of rows, number of columns, row names and column names of the CO2 dataset.
```{r}
dim(CO2)[1]
dim(CO2)[2]
row.names(CO2)
colnames(CO2)
```


